---
author: Tingwei Adeck
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: github_document
bibliography: grateful-refs.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# normfluodbf
<!-- badges: end -->

The goal of normfluodbf is to normalize fluorescence data obtained from liposome flux assay experiments via the FLUOstar microplate reader. Input or source file is a .dbf file that is not ready for analysis without processing through normfluodbf. There is a ShinyApp for this as well.

## Installation

You can install the development version of normfluodbf from [GitHub](https://github.com/AlphaPrime7/normfluodbf) with:

``` r
# install.packages("devtools")
devtools::install_github("AlphaPrime7/normfluodbf")

#Once the package makes CRAN
install.packages("normfluodbf")
library(normfluodbf)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(normfluodbf)
normalized_data <- normfluodbf("liposomes_214.dbf")
```

## R packages used
- tidyr
- data.table
- foreign
- tibble

# References
[@datatable]
[@foreign]
[@tidyverse]
