---
title: "highlights"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes/",
  out.width = "100%"
)
```

```{r echo=FALSE, results="hide", message=FALSE}
("badger")
```

[![Liposomes](https://img.shields.io/badge/Liposome%20Flux%20Assays-8A2BE2)](https://pubmed.ncbi.nlm.nih.gov/27091997/)
`r badger::badge_custom("normfluodbf", "1.5.2", "green", "https://github.com/AlphaPrime7")`
`r badger::badge_custom("Highlight", "REELS", "green", "https://github.com/AlphaPrime7")`

# 🔥 Why Highlights?

-   Sports events are filled with highlights but seldom do intellectuals like myself take time to reel in our work and find a way to document our high points. I appreciate myself and although a little dazed by this project, once the patch goes up, I will find time to enjoy and admire my work when using the package after it is re-submitted.

-   In this document, I point out highlight functions in the making of this package update. The functions that I created based on pure creativity and my proper understanding of the assay concept.

-   There are even functions that I came up with on the fly as I was troubleshooting and even I could not believe I did it. Similar to those NBA dunks that make some players feel like they just had an out of body experience.

-   I don't point out the LOWs because the process of going through making a package and seeing a major flaw immediately after publishing it is a LOW.

-   The making of the package often seems like a LOW as I run into issues in almost every step. The only win is when everything works and all test cases pass.

# 💯 resample_dat series

-   This is perhaps the most difficult part of learning to code in R while making this package.

-   I used a considerable amount of time learning how R works with this procedure and after hours and hours of understanding the R process, this function was born.

-   The pride I felt when this worked was short lived but one of my best if not best moments.

-   Below is the simplest form of that function. Several other functions on the same concept were born from this.

```{r resamples, eval=F}
resample_dat <- function(df, tnp, cycles){

  suppressWarnings({

    type_size <- c(1:tnp)
    k <- c(1:tnp)

    resulting_df <- data.frame()
    for (i in 1:(nrow(df)/tnp)){

      colnames(resulting_df) = NULL
      insert_row = df[k,]
      colnames(insert_row) = NULL

      resulting_df[i,type_size] <- rbind(insert_row, resulting_df)

      increment = tnp
      k <- k + increment
    }
    return(resulting_df)

  })

}
```

# 👌 QC

-   The QC series of functions was impressive.

-   I am SUPER PROUD of this because this function was inspired by experimental errors I commited while performing these assays myself.

-   This is my best as it showed me that I knew what I was doing and that I valued Quality above all else.

-   In fact, a lot of things in life are useless without some form of quality control that can help separate noise from signal. This function did that.

-   Also, I did this the Ubuntu way without punishing the user. This is forgiving of me given that this function took a considerable amount of time to make. I almost QUIT because of this function.

```{r qc, eval=F}
fluor_threshold_check <- function(clean_df, fun = NA){

  load.emojifont(font = "EmojiOne.ttf")

  nofun <- is.na(fun)
  clean_df <- rbind(clean_df, NA)
  clean_df <- cbind(clean_df, NA)
  for(i in 1:nrow(clean_df)){
    for(j in 1:ncol(clean_df)){
      if ( clean_df[i,j] >= (2^15) && is.na(clean_df[i,j]) != nofun ){
        message(c(emoji('pig'), emoji('camel'), emoji('lion')))
        message(paste("YIKES, value > 2^15, Watch in future experimental designs",'column:', j , 'row:', i))
      } else if ( clean_df[i,j] <= (2^11) && is.na(clean_df[i,j]) != nofun ){
        message(c(emoji('pig'), emoji('camel')))
        message(paste("YIKES, value < 2^11, Watch in future experimental designs",'column:', j , 'row:', i))
      }
    }
  }
}
```

# 💣 actual_cols_used()

-   Perhaps one of the last main functions this package needed.

-   My initial approach was to have the user provide this data but after several hiccups making the package, I realized that the data had this information. On the spot I whipped up this package which was super useful.

-   This again was another GREAT HIGH.

```{r acu, eval=F}
actual_cols_used <- function(dat){
  df <- utils::read.table(dat)
  df <- clean_odddat_optimus(df)
  colnames(df) <- c(1:ncol(df))
  acu <- names(which(colSums(!is.na(df)) > 0))
  acu <- as.numeric(as.vector(acu))

  return(acu)
}
```

# ⌛ Final Remarks

-   The culmination of all these functions into normfluodat is a high moment but it does not beat developing the subordinate functions that helped make the main function. Every moment I needed a subordinate function highlighted their power in the package and my HIGHEST moment was referencing my OWN subordinate functions into main processes within the package; this feeling was surreal.

-   The final result is often expected when work is put into the little things or sub-processes upon which the main process is dependent upon.

-   I am proud of the final recipe normfluodat but this will NOT top some of these ingenious moments when I thought of and cultivate the pieces needed to get to the final product.

-   Hope anyone that stumbles upon the page for this package gets to read and take this in.

-   Well Done to Myself!! Moving on to another big project.
